Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{Identify applicable funding agency here. If none, delete this.}

### 2023-05-16 paper-2023-acsos-pulverization.tex
revise listing 2

The second domain-specific language allows to define the concrete implementation of each component associating it to a specific start host;
moreover, it allows to define the creteria on which the system should be reconfigured by specifying which events should trigger a reconfiguration.
%
This DSL binds the more abstrac definition specified in the previous DSL to the topology of the available infrastracture,
defining the actual deployment of the system, and the reconfiguration policies.
%
The~\Cref{lst:runtime-configuration} provides an example of the usage of the domain-specific language where is defined the runtime configuration of the system.
%
The framework define the concept of \texttt{Host} that is the representation of an available physical host where the components can be deployed;
for each host is possible to specify the capabilities that it implements.
%
In this way, the framework can check if a host can execute a component by verifying if the host implements the required capabilities.
%
The runtime is configured be specifying for each implementation of a \emph{component},
its associated startup host enabling the definition of the initial deployment of the system.
%
The most relevant part of the domain-specific language, is the definition of the reconfiguration rules:
the framework models the concept of \texttt{ReconfigurationEvent}
that is the event that triggers the reconfiguration of the system.
%
The DSL allows the association of a \texttt{ReconfigurationEvent}
to a new deployment of the system which is defined as the new association between component and host.

>>>>

The second \ac{dsl} supports the definition of the mapping between pulverised components and specific hosts,
as well as the definition of reactive reconfiguration policies.
%
The~\Cref{lst:runtime-configuration} provides an example of the usage of the domain-specific language where is defined the runtime configuration of the system.
%
The framework define the concept of \texttt{Host} that is the representation of an available physical host where the components can be deployed;
for each host is possible to specify the capabilities that it implements.
%
In this way, the framework can check if a host can execute a component by verifying if the host implements the required capabilities.
%
The runtime is configured be specifying for each implementation of a \emph{component},
its associated startup host enabling the definition of the initial deployment of the system.
%
The most relevant part of the domain-specific language, is the definition of the reconfiguration rules:
the framework models the concept of \texttt{ReconfigurationEvent}
that is the event that triggers the reconfiguration of the system.
%
The DSL allows the association of a \texttt{ReconfigurationEvent}
to a new deployment of the system which is defined as the new association between component and host.
